Wealth dynamics in the presence of network structure and primitive cooperation

### 2019-06-25 manuscript/draftcssa19.tex
minor

>>>>

The current work originated in our attempts to incorporate and tease out the effects of social structures in simple models of wealth dynamics in the presence of environmental stochasticity, and a simple form of resource pooling. These models were inspired by our search for analogs of grid world agent based models of Srikanth and Milton \footnote{Include proper citation of SriMil here} where foraging agents that pool their resources were shown to on-average outperform non-pooling agents. While interaction or mixing of agent population is achieved through foraging in the original model, the model presented here achieves this by partially mixing the agents via a static network structure.

The original model drew its inspiration from historical sociology, in Katz's influential study of middle of 19th century Hamilton, Canada. Retaining this original motivation, we draw additional inspiration from economic sociology, in the work of Grannovetter; urban sociology, in the work of Sampson and others; and in anthropology, in the work on cooperation in small to medium scale societies.
